---
title: "Case Study 1 - Beers"
authors: "Nicholas Sager & Steven Cox"
date: "2/17/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Case Study 1 - Beers

## Introduction

Write an introduction.. The data set used is the Beers data set. The data set contains information on 2410 different beers from 558 different breweries in 50 different states. The data set contains information on the name of the beer, the name of the brewery, the state where the brewery is located, the alcohol by volume (ABV) of the beer, the International Bitterness Units (IBU) of the beer, and the syle of the beer.

## Read the Data
```{r}
library(tidyverse)
library(ggthemes)

beers <- read.csv("Data/Beers.csv")
breweries <- read.csv("Data/Breweries.csv")

# Verify same levels for merging with Brewery ID
str(as.factor(beers$Brewery_id))
str(as.factor(breweries$Brew_ID))

# Merge the beers and breweries data sets
beers_breweries <- left_join(beers, breweries, by = c("Brewery_id" = "Brew_ID")) %>%
    rename(Beer_Name = Name.x, Brewery = Name.y)

# Verify data frame
head(beers_breweries, 6)
tail(beers_breweries, 6)

# Noticed extra spaces in State abbr
beers_breweries$State <- str_replace_all(beers_breweries$State," ","")

```

## Data Exploration
1. How many breweries are present in each state?
```{r}
beers_breweries %>%
    group_by(State) %>%
    summarize(count = n_distinct(Brewery)) %>%
    arrange(desc(count))

beers_breweries %>%
    group_by(State) %>%
    summarize(count = n_distinct(Brewery_id)) %>%
    arrange(desc(count))
#Need to figure out why those are different. 
#Check that the number of breweries match the number of brewery ids
n_distinct(beers_breweries$Brewery) == n_distinct(beers_breweries$Brewery_id)

#View abnormalities between Brewery Name and Brewery ID
unique(beers_breweries[c("Brewery", "Brewery_id")]) %>% 
  group_by(Brewery) %>% 
  filter(n() > 1) 

duplicate_IDs <- beers_breweries %>% 
  distinct(Brewery_id, .keep_all = TRUE) %>%  #get all the unique brewery_id
  group_by(Brewery) %>% filter(n() > 1) %>%   #group by name and filter for more than 1
  summarize(Brewery_id = paste(Brewery_id, collapse = "-")) #combine id's with a "-"

# loop through entire data set and if the brewery name is in the clean_breweries list
# then change the brewery id to the combined brewery id from above
i<-0
for (name in beers_breweries$Brewery) {
  i<-i+1
  if (name %in% duplicate_IDs$Brewery) {
    j = which(name == duplicate_IDs$Brewery)
    beers_breweries$Brewery_id[i] <- duplicate_IDs$Brewery_id[j]
  }
}
#Re-check that the number of breweries match the number of brewery ids
n_distinct(beers_breweries$Brewery) == n_distinct(beers_breweries$Brewery_id)

# Plot the number of breweries in each state
library(usmap)
library(ggplot2)
library(ggthemes)

# Setup Stat for graphs
Brewery_Stat = beers_breweries %>%
  group_by(State) %>%
  summarize(count = n_distinct(Brewery)) %>%
  arrange(desc(count)) 

# Basic Bar plot
ggplot(Brewery_Stat, aes(x = reorder(State, -count), y = count)) +
    geom_bar(stat = "identity") +
    labs(x = "State", y = "Number of Breweries", title = "Number of Breweries in Each State") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))

# Heatmap of with the count over US map
df <- merge(statepop,Brewery_Stat, by = c("abbr"= "State"))
df <- left_join(statepop, Brewery_Stat, by = c("abbr"= "State"))

plot_usmap(data = df, values = "count") + 
  labs(title = "Heat Map of Breweries in Each State") + 
  theme(plot.title = element_text(hjust = 0.5), legend.position = "right") +
  scale_fill_gradient('count',  low = "lightblue", high = "red")

```

2. Merge the datasets and print the first 6 and last 6.
```{r}
# Duplicated from Wrangling section. Included here for completeness
# str(as.factor(beers$Brewery_id))
# str(as.factor(breweries$Brew_ID))
# beers_breweries <- left_join(beers_clean, breweries, by = c("Brewery_id" = "Brew_ID")) %>%
#    rename(Beer_Name = Name.x, Brewery = Name.y)

head(beers_breweries, 6)
tail(beers_breweries, 6)
```

3. Address the missing values in each column.
```{r}
#Investigate the missing values
sapply(beers_breweries, function(x) sum(is.na(x)))

# Missing style of beer
beers %>%
    group_by(Style) %>%
    summarize_all(~ sum(is.na(.))) %>%
    arrange(desc(IBU))

#Impute the values for the missing IBU values with the mean IBU value for the style of beer
beers_clean <- beers %>%
    group_by(Style) %>%
    mutate(IBU = ifelse(is.na(IBU), mean(IBU, na.rm = TRUE), IBU))

# Print the beers which have a NA value for the ABV
beers_clean %>%
    filter(is.na(ABV)) %>%
    group_by(Style) %>%
    summarize(count = n()) %>%
    arrange(desc(count))
# Need to decide what to do with these. moving on for now.

```

4. Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.
```{r}
beers_medians <-
    beers_breweries %>%
    group_by(State) %>%
    summarize(median_ABV = median(ABV, na.rm = TRUE), median_IBU = median(IBU, na.rm = TRUE)) %>%
    arrange(desc(median_ABV))

beers_medians %>%
    ggplot(aes(x = State, y = median_ABV)) +
    geom_bar(stat = "identity", fill = "cornflowerblue") +
    labs(x = "State", y = "Median Alcohol Content", title = "Median Alcohol Content in Each State") +
    theme_economist() +
    theme(axis.text.x = element_text(angle = 70, hjust = 0))

print(beers_medians)
```

5. Which state has the maximum alcoholic (ABV) beer? Which state has the most bitter (IBU) beer?
```{r}
beers_breweries %>%
    filter(ABV == max(beers_breweries$ABV, na.rm = TRUE)) %>%
    select(State, Beer_Name, ABV, Brewery)

beers_breweries %>%
    filter(IBU == max(beers_breweries$IBU, na.rm = TRUE)) %>%
    select(State, Beer_Name, IBU, Brewery)

#Less elegant, but also works
max_value <- max(beers_breweries$ABV, na.rm = TRUE)
beers_breweries[which(beers_breweries$ABV == max_value), c("State", "Beer_Name", "ABV", "Brewery")]
```

6. Comment on the summary statistics and distribution of the ABV variable.
```{r}
summary(beers_breweries$ABV, na.rm = TRUE)

beers_breweries %>% 
  group_by(Style) %>% 
  summarize(
    count = n(),
    mean = mean(ABV, na.rm = TRUE),
    sd = sd(ABV, na.rm = TRUE),
    min = min(ABV, na.rm = TRUE),
    median = median(ABV, na.rm = TRUE),
    max = max(ABV, na.rm = TRUE)
  )
```
Add comments here

7. Is there an apparent relationship between the bitterness of the beer and its alcoholic content? Draw a scatter plot.  Make your best judgment of a relationship and EXPLAIN your answer.
```{r}
beers_breweries %>%
    ggplot(aes(x = ABV, y = IBU, color = Style)) +
    geom_point(show.legend = FALSE) +
    geom_smooth(method = "lm", se = FALSE, color = "black") +
    labs(x = "Alcohol Content (ABV)", y = "Bitterness (IBU)", title = "Alcohol Content vs. Bitterness") +
    theme_minimal()
```
Explanation here

8. Budweiser would also like to investigate the difference with respect to IBU and ABV between IPAs (India Pale Ales) and other types of Ale (any beer with “Ale” in its name other than IPA).  You decide to use KNN classification to investigate this relationship.  Provide statistical evidence one way or the other. You can of course assume your audience is comfortable with percentages … KNN is very easy to understand conceptually. 
In addition, while you have decided to use KNN to investigate this relationship (KNN is required) you may also feel free to supplement your response to this question with any other methods or techniques you have learned.  Creativity and alternative solutions are always encouraged. 
```{r}
#Filter the data into a training set containing only (IPA or Ale)

#Use string methods to make an indicator of whether the beer is an IPA or an Ale (Response variable)

#Use KNN to classify the beers into IPAs and Ales using ABV and IBU as the predictors

#Print the confusion matrix and calculate the accuracy of the model

```