---
title: "Case Study 1 - Beers"
author: "Nicholas Sager"
date: "2/17/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Case Study 1 - Beers

## Introduction

Write an introduction.. The data set used is the Beers data set. The data set contains information on 2410 different beers from 558 different breweries in 50 different states. The data set contains information on the name of the beer, the name of the brewery, the state where the brewery is located, the alcohol by volume (ABV) of the beer, the International Bitterness Units (IBU) of the beer, and the syle of the beer.

## Read the Data
```{r}
library(tidyverse)
library(ggthemes)

beers <- read.csv("Data/Beers.csv")
breweries <- read.csv("Data/Breweries.csv")

summary(is.na(beers))
summary(is.na(breweries))

#Investigate the missing values by style of beer
beers %>%
    group_by(Style) %>%
    summarize_all(~ sum(is.na(.))) %>%
    arrange(desc(IBU))
```

## Data Wrangling
```{r}
#Impute the values for the missing IBU values with the mean IBU value for the style of beer
beers_clean <- beers %>%
    group_by(Style) %>%
    mutate(IBU = ifelse(is.na(IBU), mean(IBU, na.rm = TRUE), IBU))

# Print the beers which have a NA value for the ABV
beers_clean %>%
    filter(is.na(ABV)) %>%
    group_by(Style) %>%
    summarize(count = n()) %>%
    arrange(desc(count))
# Need to decide what to do with these. moving on for now.

# Merge the beers and breweries data sets
str(as.factor(beers$Brewery_id))
str(as.factor(breweries$Brew_ID))
beers_breweries <- left_join(beers_clean, breweries, by = c("Brewery_id" = "Brew_ID")) %>%
    rename(Beer_Name = Name.x, Brewery = Name.y)

head(beers_breweries)
```

## Data Exploration
1. How many breweries are present in each state?
```{r}
beers_breweries %>%
    group_by(State) %>%
    summarize(count = n_distinct(Brewery)) %>%
    arrange(desc(count))

beers_breweries %>%
    group_by(State) %>%
    summarize(count = n_distinct(Brewery_id)) %>%
    arrange(desc(count))
#Need to figure out why those are different. 
#Found duplicate for Colorado
#      Brewery            Brewery_id
# Oskar Blues Brewery        167
# Oskar Blues Brewery        504

# Plot the number of breweries in each state
beers_breweries %>%
    group_by(State) %>%
    summarize(count = n_distinct(Brewery)) %>%
    arrange(desc(count)) %>%
    ggplot(aes(x = reorder(State, -count), y = count)) +
    geom_bar(stat = "identity") +
    labs(x = "State", y = "Number of Breweries", title = "Number of Breweries in Each State") +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

2. Merge the datasets and print the first 6 and last 6.
```{r}
# Duplicated from Wrangling section. Included here for completeness
str(as.factor(beers$Brewery_id))
str(as.factor(breweries$Brew_ID))
beers_breweries <- left_join(beers_clean, breweries, by = c("Brewery_id" = "Brew_ID")) %>%
    rename(Beer_Name = Name.x, Brewery = Name.y)

head(beers_breweries, 6)
tail(beers_breweries, 6)
```

3. Address the missing values in each column.
```{r}
#Impute the values for the missing IBU values with the mean IBU value for the style of beer
beers_clean <- beers %>%
    group_by(Style) %>%
    mutate(IBU = ifelse(is.na(IBU), mean(IBU, na.rm = TRUE), IBU))

# Print the beers which have a NA value for the ABV
beers_clean %>%
    filter(is.na(ABV)) %>%
    group_by(Style) %>%
    summarize(count = n()) %>%
    arrange(desc(count))
# Need to decide what to do with these. moving on for now.

```

4. Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.
```{r}
beers_medians <-
    beers_breweries %>%
    group_by(State) %>%
    summarize(median_ABV = median(ABV, na.rm = TRUE), median_IBU = median(IBU, na.rm = TRUE)) %>%
    arrange(desc(median_ABV))

beers_medians %>%
    ggplot(aes(x = State, y = median_ABV)) +
    geom_bar(stat = "identity", fill = "cornflowerblue") +
    labs(x = "State", y = "Median Alcohol Content", title = "Median Alcohol Content in Each State") +
    theme_economist() +
    theme(axis.text.x = element_text(angle = 70, hjust = 0))

print(beers_medians)
```

5. Which state has the maximum alcoholic (ABV) beer? Which state has the most bitter (IBU) beer?
```{r}
beers_breweries %>%
    filter(ABV == max(beers_breweries$ABV, na.rm = TRUE)) %>%
    select(State, Beer_Name, ABV, Brewery)

beers_breweries %>%
    filter(IBU == max(beers_breweries$IBU, na.rm = TRUE)) %>%
    select(State, Beer_Name, IBU, Brewery)

#Less elegant, but also works
max_value <- max(beers_breweries$ABV, na.rm = TRUE)
beers_breweries[which(beers_breweries$ABV == max_value), c("State", "Beer_Name", "ABV", "Brewery")]
```

6. Comment on the summary statistics and distribution of the ABV variable.
```{r}
summary(beers_breweries$ABV, na.rm = TRUE)

beers_breweries %>% 
  group_by(Style) %>% 
  summarize(
    count = n(),
    mean = mean(ABV, na.rm = TRUE),
    sd = sd(ABV, na.rm = TRUE),
    min = min(ABV, na.rm = TRUE),
    median = median(ABV, na.rm = TRUE),
    max = max(ABV, na.rm = TRUE)
  )
```
Add comments here

7. Is there an apparent relationship between the bitterness of the beer and its alcoholic content? Draw a scatter plot.  Make your best judgment of a relationship and EXPLAIN your answer.
```{r}
beers_breweries %>%
    ggplot(aes(x = ABV, y = IBU, color = Style)) +
    geom_point(show.legend = FALSE) +
    geom_smooth(method = "lm", se = FALSE, color = "black") +
    labs(x = "Alcohol Content (ABV)", y = "Bitterness (IBU)", title = "Alcohol Content vs. Bitterness") +
    theme_minimal()
```
Explanation here

8. Budweiser would also like to investigate the difference with respect to IBU and ABV between IPAs (India Pale Ales) and other types of Ale (any beer with “Ale” in its name other than IPA).  You decide to use KNN classification to investigate this relationship.  Provide statistical evidence one way or the other. You can of course assume your audience is comfortable with percentages … KNN is very easy to understand conceptually. 
In addition, while you have decided to use KNN to investigate this relationship (KNN is required) you may also feel free to supplement your response to this question with any other methods or techniques you have learned.  Creativity and alternative solutions are always encouraged. 
```{r}
#Filter the data into a training set containing only (IPA or Ale)

#Use string methods to make an indicator of whether the beer is an IPA or an Ale (Response variable)

#Use KNN to classify the beers into IPAs and Ales using ABV and IBU as the predictors

#Print the confusion matrix and calculate the accuracy of the model

```